Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-04-11 manuscript/supplementaryRW.Rmd
added model resources for Landis in the supplementary

The most complete reference resource for the iLand regeneration module is:
Seidl, R., Spies, T. a. T. A. T. a., Rammer, W., Steel, E. A. A., Pabst, R. J. R. J. R. J., & Olsen, K. (2012). Multi-scale Drivers of Spatial Variation in Old-Growth Forest Carbon Density Disentangled with Lidar and an Individual-Based Landscape Model. Ecosystems, 15(8), 1321-1335. https://doi.org/10.1007/s10021-012-9587-2

@@

@@

\newpage
## Total ingrowth and individual species regeneration niches

>>>>

The most complete reference resource for the iLand regeneration module
is: Seidl, R., Spies, T. a. T. A. T. a., Rammer, W., Steel, E. A. A.,
Pabst, R. J. R. J. R. J., & Olsen, K. (2012). Multi-scale Drivers of
Spatial Variation in Old-Growth Forest Carbon Density Disentangled with
Lidar and an Individual-Based Landscape Model. Ecosystems, 15(8),
1321-1335. <https://doi.org/10.1007/s10021-012-9587-2>

@@

The most complete reference resources for the LANDIS-II model and
regeneration module used here are:

-   Scheller et al. 2007 -
    <https://doi.org/10.1016/j.ecolmodel.2006.10.00>
-   De Bruijn et al. 2014 -
    <https://doi.org/10.1016/j.ecolmodel.2014.05.004>
-   Petter et al. 2020 - <https://doi.org/10.1016/j.envsoft.2020.104844>
    (supplementary material)
-   User guide for PNET 4.1 online -
    <https://github.com/LANDIS-II-Foundation/Extension-PnET-Succession/blob/master/deploy/docs/LANDIS-II%20PnET-Succession%20v4.1%20User%20Guide.pdf>

@@

## Total ingrowth and individual species regeneration niches
